Thermal reactionome of a temperate ant species

### 2014-05-14 doc/ApTranscriptome_manuscript.Rmd
Updated manuscript with YAML header so can render with rmarkdown. Allows direction citation using pandoc rather than having to run separately.
Minor updates to text.

---
title: "Thermal reactionome of a temperate ant species"
author: "John Stanton-Geddes, Andrew Nguyen, Mahesh Vangala, Jim Vincent, Rob Dunn,
  Aaron Ellison, Nate Sanders, Nick Gotelli, Sara Helms-Cahan"
output:
  pdf_document:
    fig_caption: yes
    latex_engine: xelatex
  html_document: null
bibliography: ApTranscriptome.bib
csl: ecology.csl
---

@@

The Trinity *de novo* transcriptome assembly included 126,172 genes with a total length of 100 million bp. Filtering to remove redundant or chimeric reads resulted in an assembly with 105,536 genes. The total length was 63 million bp with an N~50~ length of 895 bp and a mean gene size of 593 bp. Of the 105,536 filtered genes, 55,432 had hits to the NCBI-nr database. Of these, 38,711 genes mapped to GO terms, 1,659 genes were identified to an enzyme and 18,935 genes mapped to a domain with >50% coverage. DeconSeq identified 5,675 genes as known contaminants from human, virus, bacterial or archael sources, leaving 99,861 clean transcripts. Of these, 47% have best hits to genes from the class Insecta [Supplementary Krona plot](http://johnstantongeddes.org/assets/files/ApTranscriptome_FA.html).

>>>>

---
title: "Thermal reactionome of a temperate ant species"
author: "John Stanton-Geddes, Andrew Nguyen, Mahesh Vangala, Jim Vincent, Rob Dunn,
  Aaron Ellison, Nate Sanders, Nick Gotelli, Sara Helms-Cahan"
csl: ecology.csl
output:
  pdf_document:
    fig_caption: yes
    latex_engine: xelatex
  html_document: null
bibliography: ApTranscriptome.bib
---

@@

The Trinity *de novo* transcriptome assembly included 126,172 genes with a total length of 100 million bp. Filtering to remove redundant or chimeric reads resulted in an assembly with 96,253 contigs and a total of 105,536 genes. For all genes, the total length was 63 million bp with an N~50~ length of 895 bp and a mean contig size of 593 bp. Of the 105,536 filtered genes, 55,432 had hits to the NCBI-nr database. Of these, 38,711 genes mapped to GO terms, 1,659 genes were identified to an enzyme and 18,935 genes mapped to a domain with >50% coverage. DeconSeq identified 5,675 genes as known contaminants from human, virus, bacterial or archael sources, leaving 99,861 clean transcripts. Of these, 47% have best hits to genes from the class Insecta.
